---
title: "7.new.Russ_1618"
author: "Danny"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(foreign)
library(haven)
library(tidyverse)
library(summarytools)
library(readxl)
options(scipen = 999)
```


# set up data
```{r import, message=FALSE, warning=FALSE, include=FALSE}


### To get earned_units in carnegie (divide by 6)

sheetnum <- (1:6)
cc1618 <- lapply(sheetnum, function(x)read_excel("C:/Users/katzd/Downloads/7.new.GFSF_16_18.xlsx", sheet = x))

lapply(cc1618, names)


cc1618_courses <- cc1618[[3]]


cc1618_attend <- cc1618[[2]]
View(cc1618_attend)

cc1618_grade <- cc1618[[1]]
cc1618_grade <- cc1618_grade[-1, ]

ccenroll <- cc1618[[6]]
cccourse <- cc1618[[5]]
n_distinct(cccourse$SSID)


ccvals <- cc1618_grade %>% filter(SSID == "2162556372") %>%
  dplyr::select(SSID, InterSegmentKey) %>%
  left_join(., cccourse, by = "SSID")

ccvals2 <- cc1618_grade %>% filter(SSID == "6138453284") %>%
  dplyr::select(SSID, InterSegmentKey) %>%
  left_join(., cccourse, by = "InterSegmentKey")


n_distinct(cc1618_grade$SSID)

not910 <- cc1618_grade %>%
  filter(GradeCode != "09" & GradeCode != "10")
n_distinct(not910$SSID)

just9 <- cc1618_grade %>%
  filter(GradeCode=="09")

n_distinct(just9$SSID)

just10 <- cc1618_grade %>%
  filter(GradeCode=="10")


n_distinct(just10$SSID)


in9ththnot10th <- anti_join(just9, just10, by = "SSID")

n_distinct(in9ththnot10th$SSID)


cdss <- c("1975713",
"2365540",
"5575184",
"4770250",
"3667710",
"3467355",
"2465755",
"5872736",
"1673932",
"4670177",
"1162653",
"1965052",
"5376513",
"5772694")

cc1618_grade <- cc1618_grade %>% mutate(subcds = substr(CDS, 1, 7)) %>%
  mutate(eval_school = if_else(subcds %in% cdss, 1, 0))

justeval_sum <- cc1618_grade %>%
  filter(YearCode=="2017-2018", GradeCode=="10") %>%
  group_by(subcds) %>%
  summarise(eval_tot=n_distinct(SSID)) %>%
  filter(subcds %in% cdss)

write.csv(justeval_sum, "studentspercds.csv")



paste("there are", n_distinct(cc1618_grade$SSID), "unique total students (cases)", sep = " ")


# have to get the right cohort and add a group number by SSID, YearCode, GradeCode. 
cc1618_g910 <- cc1618_grade %>%  
  filter(YearCode=="2016-2017" & GradeCode=="09"| YearCode=="2017-2018" & GradeCode=="10"  ) %>%
  group_by(SSID, YearCode, GradeCode) %>%
  mutate(dup_SSID = n_distinct(CDS)) %>%
  mutate(group_id = row_number() ) %>%
  ungroup() %>%
  group_by(SSID) %>%
  mutate(total_school = n_distinct(CDS))



##cc1618_g10 <- cc1618_g910 %>%  
 # filter(YearCode=="2017-2018" & GradeCode=="10") %>%
 # group_by(SSID) %>%
 # mutate(dup_SSID = n_distinct(CDS)) %>%
 # mutate(group_id = row_number() )
#


cc1618_g910_d <- cc1618_g910 %>%
  filter(group_id==1) %>%
  mutate(multiple_cds = ifelse(dup_SSID>1, 1, 0))

cc1618_g910_duplicate <- cc1618_grade %>%
filter(YearCode=="2016-2017" & GradeCode=="09"| YearCode=="2017-2018" & GradeCode=="10"  ) %>%
  group_by(SSID, YearCode, CDS, GradeCode) %>%
  mutate(group_id = row_number() )


View(cc1618_g910_duplicate)

dup_flag <- cc1618_g10 %>%
  group_by(SSID) %>%
  pivot_wider(id_cols = SSID, values_from = cds, names_from = group_id, names_prefix = "cds") %>% left_join(., cc1618_g10_distinct2, by = "SSID") %>%
  select(inter_segment_key, SSID, cds1:cds4, Gender, IsHispanicEthnicity, Race01, Race02, multiple_cds)

```

## tracking down duplicates
```{r}

dup_flag <- cc1618_g10 %>%
  select(inter_segment_key, SSID, cds, dup_SSID, dup_SSID_cds, flag_mult_cds) %>%
  ungroup() %>%
  pivot_wider(id_cols = SSID, names_from = dup_SSID, values_from = cds)
 



dups <- cc1618_g10 %>% 
  mutate(inter_segment_key2 = ifelse(inter_segment_key=="NULL", NA, inter_segment_key)) %>%
  group_by(SSID) %>%
 fill(inter_segment_key2) %>%
  select(inter_segment_key, SSID, )
  ungroup() %>%
  pivot_wider(id_cols=SSID, names_from = dup_SSID, values_from = cds)
  
glimpse(dups)

paste("there are", n_distinct(cc1618_g10$SSID), "unique 10th grade students (cases)", sep = " ")

dim(cc1618_grade)

sum(duplicated(cc1618_grade$SSID))
sum(duplicated(cc1618_g10$SSID))

cc1618_g10NULL <- cc1618_g10 %>% filter(inter_segment_key=="NULL")
n_distinct(cc1618_g10NULL$SSID)


```
## Try to figure out duplicates
```{r duplicates}

cc1618dup10 <- cc1618_g10 %>% 
  group_by(SSID) %>% 
  filter(n() > 1) %>%
  summarise(n=n())
```

# Creates a dataset with just gfsf schools
```{r}
gfsf1618_dup2 <- filter(cc1618gfsfgrade_dup, subcds %in% cdss)
as.data.frame(table(gfsf1618_dup2$subcds))$Var1 %in% cdss
```

```{r}

table(gfsf1618_dup$subcds)
n_distinct(gfsf1618_dup)

dupgfsf <- left_join(gfsf1618_dup, cc1618dup10, by = "SSID")

table(dupgfsf$subcds)
```
## Get the full 10th grade dataset 
```{r attendance, include=FALSE}
library(tidyverse)

# Get High School attend Data ###

cc1618_attend_agg <- cc1618_attend %>%
  filter(SSID != "(15007 rows affected)") %>%
  group_by(SSID, YearCode) %>%
  summarize(tot_attend = sum(AttendedDays),
            tot_expect_attend = sum(ExpectedAttendanceDays),
            attendrate = tot_attend/tot_expect_attend,
            suspendtot = sum(SuspendedDays),
            suspend_rate = sum(SuspendedDays)/sum(tot_expect_attend),
            chron_abs = if_else(attendrate <= .9, 1, 0))

GFSFschools <- read_excel("C:/Users/katzd/Desktop/Rprojects/GFSF/GFSFschools.xlsx")
GFSFschools <- GFSFschools[-c(11, 22), ] %>%
  select(CDS:FFF)
names(GFSFschools)
GFSFschools2 <- read_sav("C:/Users/katzd/Downloads/Evaluation schools 1516 data (J=20).sav") %>%
  mutate(cds = as.character(cds))

names(GFSFschools2)[1:4] <- c("CDS",                         "High School",                 "District",                   "FFF")

GFSFschools2 <- GFSFschools2 %>% 
  select(CDS:FFF)

# get just first CDS from attend

CDS_attend <- cc1618_attend %>%
  filter(YearCode=="2016-2017") %>% 
  full_join(., GFSFschools2, by = "CDS") %>%
  mutate(GFSF_FFF_attend = case_when(
  FFF==0 ~"0",
  FFF==1 ~ "1")) %>%
  group_by(SSID) %>%
  mutate(FFF_any = if_else(any(GFSF_FFF_attend==1)|any(GFSF_FFF_attend==2), 1, 0)) %>%
  filter(FFF_any == 1 & GFSF_FFF_attend == 1 | FFF_any == 0 & GFSF_FFF_attend ==0|is.na(FFF_any)&is.na(GFSF_FFF_attend)) %>%
  mutate(id = row_number()) %>%
  filter(id==1) %>%
  ungroup() %>%
  select(SSID, CDS, FFF) %>%
  rename("attend_CDS" = CDS, "attend_FFF"=FFF)

n_distinct(cc1618_attend$SSID)
n_distinct(CDS_attend$SSID)

CDS_attend[CDS_attend$SSID %in% cc1618_attend$SSID==F,  ]

summary(cc1618_attend_agg[cc1618_attend_agg$YearCode=="2017-2018", ])

```
```{r}
# Get enrollment GFSF

CDS_enroll <- cc1618_grade %>%  
  filter(YearCode=="2016-2017" & GradeCode=="09") %>%
  full_join(., GFSFschools2, by = "CDS") %>%
  mutate(GFSF_FFF_enroll = case_when(
  FFF==0 ~"0",
  FFF==1 ~ "1")) %>%
  group_by(SSID) %>%
  mutate(FFF_any = if_else(any(GFSF_FFF_enroll==1), 1, 0)) %>%
  filter(FFF_any == 1 & GFSF_FFF_enroll == 1 | FFF_any == 0 & GFSF_FFF_enroll ==0|is.na(FFF_any)&is.na(GFSF_FFF_enroll)) %>%
  mutate(id = row_number()) %>%
  filter(id==1) %>%
  ungroup() %>%
  select(SSID, CDS, FFF) %>%
  rename("enroll_CDS" = CDS, "enroll_FFF"=FFF)



  
n_distinct(cc1618_grade$SSID)
n_distinct(CDS_enroll$SSID)

CDS_enroll[CDS_enroll$SSID %in% cc1618_grade$SSID==F,  ]

exp()

```

# this also has suspension
#hs_attend910 <- left_join(cc1618_g910_d, cc1618_attend, by = c("SSID", "YearCode", "CDS"))

```{r}
filedat_units <- cc1618_courses %>%
  mutate(GPA_points1 = recode(Grade, 
     "A"  =   "4"  ,
     "A+" =   "4"  ,
     "A-" =   "4"  ,
     "A_" =   "4"  ,
     "B"  =   "3"  ,
     "B+" =   "3"  ,
     "B-" =   "3"  ,
     "C+" =   "2"  ,
     "C"  =   "2"  ,
     "C-" =   "2"  , 
     "D+" =   "1"  ,
     "D"  =   "1"  ,
     "D-" =   "1"  ,
     "F"  =   "0"  ),
     
#if_else(CreditAttempted==5|CreditAttempted==10|CreditAttempted==2.5, CreditEarned/10, CreditEarned),
     UnitsAttempted = case_when(CreditAttempted >= 1 & CourseTerm != "FY"| 
                             CreditAttempted > 1 & CourseTerm == "FY" ~ CreditAttempted/10),
UnitsEarned = case_when(CreditAttempted >= 1 & CourseTerm != "FY"| 
                             CreditAttempted > 1 & CourseTerm == "FY" ~ CreditEarned/10),
#if_else(CreditAttempted==5|CreditAttempted==10|CreditAttempted==2.5, CreditAttempted/10, CreditAttempted),
     GPA_points1 = as.numeric(GPA_points1),
     GPA_points1 = replace_na(GPA_points1, 0),
     GPA_points = ifelse(CreditEarned/CreditAttempted==.5 & Grade=="F", .5, GPA_points1),
         #`GPA_points_fy*` = if_else(course_term == "FY", as.numeric(GPA_points)*2, `GPA_points*`,
         `fail*`=ifelse(Grade=="F" & CourseTerm =="FY" & CreditEarned==0, 2,
                        if_else(Grade == "F" & CourseTerm =="FY" & CreditEarned/CreditAttempted == .5, 1, 
                                ifelse( CourseTerm !="FY"& Grade=="F", 1, 0))),
         #`carnegie_earn*` = CreditEarned/5,
         #`carnegie_attemp*` = CreditAttempted/5,
         `ag*` = if_else(!is.na(AGstatus) & GPA_points >= 2, 1, 
                                          0),
GFSF_cred = case_when(
     str_detect(CourseTitle, "^GFSF")|
     str_detect(CourseTitle, "Life Skills")|
     str_detect(CourseTitle, "Office Practices")|
     str_detect(CourseTitle, "College and Career Ready")|
     str_detect(CourseTitle, "Future Focus")|
     str_detect(CourseTitle, "Seminar")| 
     str_detect(CourseTitle, "College Prep")|
     str_detect(CourseTitle, "Success 101")|
     str_detect(CourseTitle, "College & Car")|
     str_detect(CourseTitle, "College and Career Readiness")|
     str_detect(CourseTitle, "^BldgFnd") ~T),
AVID_cred = case_when(str_detect(CourseTitle, "^Avid")|
                      str_detect(CourseTitle,"^AVID")~T),
GFSF_UNIT_earn = case_when(GFSF_cred==T~UnitsEarned),
GFSF_UNIT_attempt = case_when(GFSF_cred==T~UnitsAttempted),
AVID_UNIT_earn = case_when(str_detect(CourseTitle, "^Avid")|
                           str_detect(CourseTitle,"^AVID")~UnitsEarned),
AVID_UNIT_attempt=case_when(str_detect(CourseTitle,"^Avid")|
                            str_detect(CourseTitle,"^AVID") ~UnitsAttempted)) %>% 
  group_by(SSID) %>%
  mutate(tot_distinct_schools=n_distinct(SSID))

indicat_SSID <- cc1618_courses %>%
  #filter(YearCode=="2016-2017") %>%
  distinct(., SSID, CDS, YearCode) %>%
  select(SSID, CDS, YearCode) %>%
  group_by(YearCode, SSID) %>%
  mutate(group_id = paste0("school_", row_number())) %>%
  ungroup() %>%
  pivot_wider(values_from = CDS, names_from = group_id)

write_sav(indicat_SSID, "just_school.sav")


  



###get credit earned basically this puts together the whole file.
indicators<- filedat_units %>%
  group_by(SSID, YearCode) %>% 
  summarize(
            GFSF_courses_taken = sum(GFSF_cred, na.rm = T),
            AVID_course_taken = sum(AVID_cred, na.rm = T),
    #`credearnraw*` = sum(CreditEarned),
            `cred_earn_carn*` = sum(UnitsEarned),
            `credit_attempt_carn*` = sum(UnitsAttempted),
            `ag_cred_earn_carn*` = sum(`ag*`*UnitsEarned),
            `ag_courses*` = sum(`ag_cred_earn_carn*`, na.rm = T),
            #`ag_cred_carn_earn*` = sum(`ag_cred_earn*`/5),
            `totfail*` = sum(`fail*`),
            `GPA*` = sum(GPA_points * UnitsEarned, na.rm=T)/sum(UnitsAttempted, na.rm = T), 
            `aggpa**` = sum(GPA_points * UnitsEarned * `ag*`)/(sum(UnitsAttempted*`ag*`)),
            GFSF_units_attempt = sum(GFSF_UNIT_attempt, na.rm=T),
            GFSF_Units_earn = sum(GFSF_UNIT_earn, na.rm=T),
            AVID_units_attempt = sum(AVID_UNIT_attempt, na.rm=T),
            AVID_Units_earn = sum(AVID_UNIT_earn, na.rm=T),
            GFSF_GPA = sum(GPA_points*GFSF_UNIT_earn,  na.rm=T)/sum(GFSF_UNIT_attempt, na.rm=T),
            AVID_GPA = sum(GPA_points*AVID_UNIT_earn,  na.rm=T)/sum(AVID_UNIT_attempt,  na.rm=T)) %>%
  mutate(`aggpa*`=if_else(is.nan(`aggpa**`), 0, `aggpa**`)) %>%
  ungroup() %>%
  group_by(SSID) %>%
  mutate(total_ag_cred_earn_carn =sum(`ag_cred_earn_carn*`, na.rm=T),
         total_ag_course = sum(`ag_courses*`, na.rm = T))

indicators_two <- filedat_units %>%
  group_by(SSID) %>%
  summarize(`total_GPA*` = sum(GPA_points * UnitsEarned/sum(UnitsAttempted, na.rm = T), na.rm=T),
            `total_ag_gpa**` = sum(GPA_points * UnitsEarned * `ag*`)/(sum(UnitsAttempted*`ag*`))) %>%
  mutate(`total_ag_gpa*`=if_else(is.nan(`total_ag_gpa**`), 0, `total_ag_gpa**`)) %>%
  select(SSID, `total_GPA*`, `total_ag_gpa*`)


indicators <- left_join(indicators, indicators_two, by="SSID")
         
  #ungroup() %>%


#GFSFschools <- bind_rows(GFSFschools, GFSFschools2)


CDS_courses<- cc1618_courses %>%
  filter(YearCode=="2016-2017") %>%
  full_join(., GFSFschools2, by = "CDS") %>%
  mutate(GFSF_FFF_courses = case_when(
    FFF==0 ~"0",
    FFF==1 ~ "1"  )) %>%
  group_by(SSID) %>%
  mutate(FFF_any = if_else(any(GFSF_FFF_courses==1), 1, 0)) %>%
  filter(FFF_any == 1 & GFSF_FFF_courses == 1 | FFF_any == 0 & GFSF_FFF_courses ==0|is.na(FFF_any)&is.na(GFSF_FFF_courses)) %>%
  mutate(id = row_number()) %>%
  filter(id==1) %>%
  ungroup() %>%
  select(SSID, CDS, FFF) %>%
  rename("courses_CDS" = CDS, "courses_FFF"=FFF)
  
##n_distinct(cc1618_courses$SSID)
#
#n_distinct(CDS_courses$SSID)
#n_distinct(CDS_courses2$SSID)
#
#
#CDS_courses[CDS_courses$SSID %in% cc1618_courses$SSID ==F, ]
```


```{r}
indicators2 <- left_join(cc1618_g910_d, indicators, by=c("SSID", "YearCode")) %>%
  group_by(SSID) %>%
  left_join(., cc1618_attend_agg, by = c("SSID", "YearCode")) %>%
  group_by(SSID, YearCode) %>%
           mutate( `ontrack1*` = ifelse(`totfail*` <= 1 & `cred_earn_carn*` >=5, 1, 0),
         `ontrack2*` = if_else(sum(attendrate) >= .95 & sum(suspendtot) ==0 & `totfail*` ==0, 1,0)) %>%
  ungroup() %>%
  group_by(SSID) %>%
  mutate(`total_ontrack1*` = ifelse(`totfail*` <= 2 & `cred_earn_carn*` >=10, 1, 0),
         `total_ontrack2*` = if_else(sum(attendrate/n()) >= .95 & sum(suspendtot) ==0 & `totfail*` ==0, 1, 0)) %>%
  ungroup() %>%
  group_by(SSID, YearCode) %>%
  mutate(gradeenroll = if_else(GradeCode=="09"|GradeCode=="10", 1, 0)) %>%
  ungroup() %>%
  group_by(SSID) %>%
  mutate(grade_both = sum(gradeenroll),
         only_1_grade = if_else(grade_both < 2, 1, 0)) %>%
  dplyr::select(-gradeenroll, -grade_both) %>%
  left_join(., CDS_attend, by=c("SSID")) %>%
  left_join(., CDS_courses, by = "SSID") %>%
  left_join(., CDS_enroll, by ="SSID") %>%
  #left_join(., indicat_SSID, by=c("SSID")) %>%
  mutate(treat = if_else(courses_FFF==1|enroll_FFF==1|attend_FFF==1, 1, 0))

names(indicators2)

indicators3 <- indicators2 %>%
  select(-group_id, -eval_school) %>%
  select(SSID, courses_CDS, enroll_CDS, attend_CDS, CDS, treat, InterSegmentKey:treat ) %>%
  rename("CDS_courses" = courses_CDS,
         "CDS_enroll" = enroll_CDS, 
         "CDS_attend" = attend_CDS,
         "num_schools_year" = dup_SSID,
         "fail" = `totfail*`,
         "attend_during_year" = tot_attend,
         "expect_attend_during_year"=tot_expect_attend,
         "suspend_year" = suspendtot) %>%
  group_by(SSID) %>%
  mutate(total_fail=sum(fail)) %>%
  select(-CDS)

names(indicators3) <- make.names(names(indicators3))


write.csv(indicators3, "student_level_variables_gfsf15.csv")
write_sav(indicators3, "student_level_variables_gfsf15.sav")


fails <- indicators3 %>%
  group_by(SSID) %>%
  summarise(total_fail=sum(fail, na.rm=T))

hist(fails$total_fail)

  

summary(indicators[indicators$YearCode=="2017-2018", ])


indicator_agg <- indicators %>% group_by(SSID) %>%
  summarize(`ag_cred_earn_carn_agg*` = sum(`ag_cred_earn_carn*`))
summary(indicator_agg)


summary(indicators)
write.csv(indicators2, "student_level_variables_gfsf6.csv")
write_sav(indicators2, "student_level_variables_gfsf6.sav")

write.csv(filedat_units, "constructed_case_level_gfsf5.csv")
write_sav(filedat_units, "constructed_case_level_gfsf5.sav")

# add total ag_course over two years
# add total failures over years 
# total = two years


fails %>%
  ggplot(., aes(x=total_fail)) + 
  geom_histogram(stat = "count")

total_gfsf <- indicators3 %>%
  filter(YearCode=="2016-2017") %>%
  group_by(CDS_courses) %>%
  summarise(total_GFSF = sum(GFSF_courses_taken))
```

```{r}

#create GPA points
cc1618full <- cccourse %>% mutate(cc_gpaval = case_when(Grade=="A"  ~  4, 
                                                       Grade== "A-" ~  4, 
                                                       Grade== "A+" ~  4, 
                                                       Grade== "B"  ~  3, 
                                                       Grade== "B-" ~  3, 
                                                       Grade== "B+" ~  3, 
                                                       Grade== "C+" ~  2, 
                                                       Grade== "C"  ~  2, 
                                                       Grade== "C-" ~  2, 
                                                       Grade== "D+" ~  1, 
                                                       Grade== "D"  ~  1, 
                                                       Grade== "D-" ~  1, 
                                                       Grade== "F"  ~  0)) %>%
  mutate(tflag_attempt  = ifelse(CreditFlag=="T" & UnitsAttempted > 0, 1, ifelse(CreditFlag=="T" & UnitsAttempted >= 88, NA, 0))) %>%
         mutate(tflag_earn  = if_else(CreditFlag=="T" &  UnitsEarned < 88 & UnitsEarned >0, 1, 0)) %>%
  mutate(t_units_attempt = tflag_attempt*UnitsAttempted,
         t_units_earned = tflag_earn*UnitsEarned,
         UCflag  = ifelse(TransferStatus=="A" & UnitsEarned <= UnitsAttempted, 1, 0),
         CSUflag  = ifelse(UCflag==1 | TransferStatus == "B"  & UnitsEarned <= UnitsAttempted, 1, 0),
         UCunits = UCflag * UnitsEarned, 
         CSUunits = CSUflag * UnitsEarned,
         fail = ifelse(Grade=="F", 1, 0),
         cflag  = ifelse(TopCode=="493012" & UnitsEarned <= UnitsAttempted, 1, 0),
         topflag  = ifelse(TopCode=="493013" & UnitsEarned <= UnitsAttempted| TopCode == "499900" & UnitsEarned <= UnitsAttempted, 1, 0),
         cflag_earn = cflag*UnitsEarned,
         topflag = topflag*UnitsEarned,
         sub_year = substr(TermId, 1, 2),
         Year_Code = if_else(TermId=="167"|TermId=="165"|TermId=="168"|TermId=="171"|TermId=="172"|TermId=="173"| TermId=="174", "2016-2017",
  ifelse(TermId=="175"|TermId=="177"|TermId=="178"|sub_year=="18", "2017-2018", "2015-2016")))




cc_var_2 <- cc1718full %>%
  group_by(SSID, Year_Code) %>%
  summarise(num_trans_attempt = sum(tflag_attempt, na.rm = T),
            num_trans_earn = sum(tflag_earn, na.rm = T),
            attemp_trans_units = sum(t_units_attempt, na.rm=T),
            earn_trans_units = sum(t_units_earned, na.rm = T),
            num_UC_attempt = sum(UCflag, na.rm=T),
            num_CSU_attempt =  sum(CSUflag, na.rm=T),
            sum_UC_earn_units = sum(UCunits, na.rm = T),
            sum_CSU_earn_units = sum(CSUunits, na.rm = T),
            earned_career_493012 = sum(cflag_earn, na.rm = T),
            earned_493013_499900 = sum(topflag, na.rm = T),
            tot_fails = sum(fail, na.rm = T),
            GPA = sum(cc_gpaval * t_units_earned, na.rm = T)/sum(t_units_attempt, na.rm=T)) %>%
  filter(SSID != "(1806 rows affected)")
  

cc_var_notyear <- cc1718full %>%
  group_by(SSID) %>%
  summarise(num_trans_attempt = sum(tflag_attempt, na.rm = T),
            num_trans_earn = sum(tflag_earn, na.rm = T),
            attemp_trans_units = sum(t_units_attempt, na.rm=T),
            earn_trans_units = sum(t_units_earned, na.rm = T),
            num_UC_attempt = sum(UCflag, na.rm=T),
            num_CSU_attempt =  sum(CSUflag, na.rm=T),
            sum_UC_earn = sum(UCunits, na.rm = T),
            sum_CSU_earn = sum(CSUunits, na.rm = T),
            earned_career_493012 = sum(cflag_earn, na.rm = T),
            earned_493013_499900 = sum(topflag, na.rm = T),
            tot_fails = sum(fail, na.rm = T)
            )

cc_var_1617 <- cc_var_2 %>%
  filter(Year_Code=="2016-2017")

write.csv(cc_var_2, "ccvars16_18_byyear.csv")

n_distinct(cc_var_2$SSID)

summary(cc_var_2[cc_var_2$Year_Code=="2017-2018",] )
View(cc_var_notyear)

no_match <- anti_join(indicators2, cc_var_2)

paste("there are", n_distinct(cc1718full$InterSegmentKey), "unique students (cases)", sep = " ")

cc1618full %>% group_by(Year_Code) %>%
  summarise(n=n(),
            total_d = n_distinct(SSID))

cc1618full %>%
  summarise(n=n(),
            ndist=n_distinct(SSID))
```



## Get transfer data
```{r transferstat}



#aggregate transfer
# get number of students with units earned
numearn <- cc1718full %>% 
  mutate(tflag  = ifelse(CreditFlag=="T" & UnitsAttempted >= .5, 1, 0)) %>% select(inter_segment_key, CreditFlag, tflag, UnitsAttempted, UnitsEarned) %>% filter(UnitsEarned < 88 & UnitsEarned > 0) %>% group_by(inter_segment_key) %>% summarise(sum(tflag))

names(tUnitsearned)[2] <- "tUnitsEarned"

summary(course_student$`sum(UnitsAttempted * tflag)`)
summary(tUnitsearned$`sum(UnitsEarned * 1)`)


table(duplicated(course_student$inter_segment_key))



#courses1617 %>% mutate(tflag  = ifelse(CreditFlag=="T", 1, 0))%>%group_by(derkey1) %>% #summarise(sum(UnitsAttempted)) %>% nrow()

#aggregate transfer type
#courses1617 %>% group_by(TransferStatus) %>% summarise(sum(UnitsAttempted))
#sum(duplicated(courses1617$derkey1))
#bystudent
#studentdat1 <- courses1617 %>% filter(CreditFlag=="T" & UnitsAttempted >= 1) %>% #group_by(derkey1) %>% summarise(sum(UnitsAttempted))

#studentdat <- courses1617 %>% group_by(derkey1) %>% summarise(sum(UnitsAttempted))

#mean(studentdat$`sum(UnitsAttempted)`)

#names(studentdat)[2] <- "transunitsattemp"

#if include students that don't take T eligible courses
#%>% mutate(tflag  = ifelse(CreditFlag=="T", 1, 0)) %>% mutate(tunits = tflag * `sum(UnitsAttempted)`) %>% group_by(derkey1) %>% summarise(sum(tunits))

#range(studentdat$`sum(UnitsAttempted)`)

#make sure the totals match
#colSums(studentdat[2])


# to merge studentdat
```


```{r}
#aggregate transfer type
##to merge UC_CSUearned

#courses1617 %>% group_by(TransferStatus) %>% summarise(sum(UnitsEarned))

# getting UC vs CSU conditioning on T
UC_CSUearned <- cc1718full %>%  filter(CreditFlag=="T" & UnitsAttempted >= 1) %>%
    mutate(UCflag  = ifelse(TransferStatus=="A" & UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(CSUflag  = ifelse(UCflag==1 | TransferStatus == "B" & UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(UCunits = UCflag * UnitsEarned, CSUunits = CSUflag * UnitsEarned) %>% 
  group_by(inter_segment_key) %>% summarise(sum(UCunits), sum(CSUunits))

summary(UC_CSUearned)

# Not conditioning on attempting any transferable unit

UC_CSUearned2 <- cc1718full %>%
    mutate(UCflag  = ifelse(TransferStatus=="A" & UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(CSUflag  = ifelse(UCflag==1 | TransferStatus == "B" & UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(UCunits = UCflag * UnitsEarned, CSUunits = CSUflag * UnitsEarned) %>% 
  group_by(inter_segment_key) %>% summarise(UC_units=sum(UCunits), CSU_Units = sum(CSUunits))
# getting UC vs CSU NOT conditioning on T

summary(UC_CSUearned2)

UC_CSUearned <- cc1718full  %>%
    mutate(UCflag  = ifelse(TransferStatus=="A" &  UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(CSUflag  = ifelse(UCflag==1 | TransferStatus == "B"  & UnitsEarned <= UnitsAttempted, 1, 0)) %>% mutate(UCunits = UCflag * UnitsEarned, CSUunits = CSUflag * UnitsEarned) %>% 
  group_by(inter_segment_key) %>% summarise(sum(UCunits), sum(CSUunits))

summary(UC_CSUearned)

#this creates indicators for how many and if UC/CSU attempted
UC_CSUindicator <- cc1718full %>% mutate(UCCSUattempt = ifelse(TransferStatus=="A", 1, 0), CSUattempt = ifelse(TransferStatus=="B", 1, 0), nottransfer =ifelse(TransferStatus=="C", 1, 0), basicskills = ifelse(CreditFlag=="S", 1, 0)) %>% group_by(inter_segment_key) %>% summarise(UCSCUattempt1 = sum(UCCSUattempt), CSUattempt1=sum(CSUattempt), notransfer1 = sum(nottransfer), basicskills1=sum(basicskills)) %>% mutate(UCCSUattemptflag = ifelse(UCSCUattempt1>0, 1, 0), CSUattempt1flag = ifelse(CSUattempt1>0, 1, 0), nottransferattemptflag = ifelse(notransfer1 >0, 1, 0), basicskillsindic = ifelse(basicskills1 >0, 1, 0))

View(UC_CSUindicator)

summary(UC_CSUindicator)



mean(UC_CSUearned$`sum(CSUunits)`)

#to merge UC_CSUearned

```

```{r career credtits}
#493012
cc1718full$TopCode <- as.character(cc1718full$TopCode)

table(cc1718full$TopCode)

## Careerearned <- cc1718full %>%  filter(CreditFlag=="T" & UnitsAttempted >= 1) %>%
#    mutate(cflag  = ifelse(TopCode==493012 & UnitsEarned <= UnitsMax, 1, 0))%>% 
#  group_by(inter_segment_key, cflag) %>% summarise(sum(UnitsEarned)) %>% mutate(cunits =  #cflag * `sum(UnitsEarned)`) %>% group_by(derkey1) %>% summarise(sum(cunits))

sum(duplicated(Careerearned$derkey1)==T)

range(Careerearned$`sum(cunits)`)


Careerearned <- cc1718full %>%
    mutate(cflag  = ifelse(TopCode==493012 & UnitsEarned <= UnitsAttempted, 1, 0))%>% 
  group_by(inter_segment_key) %>% summarise(TOP_493012= sum(UnitsEarned*cflag)) 


# filter by attempted (among)
Careerearned <- cc1718full %>% filter(CreditFlag=="T") %>%
    mutate(cflag  = ifelse(TopCode==493012 & UnitsEarned <= UnitsAttempted, 1, 0))%>% 
  group_by(inter_segment_key) %>% summarise(sum(UnitsEarned*cflag)) 

#%>% mutate(cunits = cflag * `sum(UnitsEarned)`) %>% group_by(derkey1) %>% summarise(sum(cunits))


#to merge CareerEarned#

summary(Careerearned)


```

```{r failed courses}

# Get just students who attempted a transfer eligible course
Transferdat <- cc1718full %>% filter(CreditFlag == "T")
nrow(Transferdat)

failT <- Transferdat %>% mutate(fail = ifelse(Grade == "F"|Grade=="NC/NP", 1, 0)) %>% group_by(inter_segment_key) %>% summarise(sum(fail))

summary(failT)

# redo it with students whether course transfer elegible or not
failT2 <- cc1718full %>% mutate(fail = ifelse(Grade == "F"|Grade=="NC/NP", 1, 0)) %>% group_by(inter_segment_key) %>% summarise(total_fail=sum(fail))

summary(failT2)
sum(failT$`sum(fail)`, na.rm = T)

mean(failT$`sum(fail)`)
colSums(failT[2])

sum(duplicated(failT$derkey1)==T)

#to merge, failT2
```

```{r 493013 499900}
# top earned not selecting on attempts
topearned <- cc1718full %>%
    mutate(cflag  = ifelse(TopCode==493013 & UnitsEarned <= UnitsAttempted|TopCode==499900 & UnitsEarned <= UnitsAttempted, 1, 0))%>% 
  group_by(inter_segment_key) %>% 
  summarise(successcredits = sum(UnitsEarned*cflag)) 
summary(Careerearned)

## DONT USE FOR NOW ###
topearned <- cc1718full %>% filter(CreditFlag=="T" & UnitsAttempted >= 1) %>%
    mutate(topflag  = ifelse(TopCode==493013 & UnitsEarned <= UnitsAttempted| TopCode == 499900 & UnitsEarned <= UnitsAttempted, 1, 0))%>% 
  group_by(inter_segment_key, topflag) %>% summarise(sum(UnitsEarned)) %>% mutate(topunits = topflag * `sum(UnitsEarned)`) %>% group_by(inter_segment_key) %>% summarise(sum(topunits))

summary(topearned)

# top earned seperate
topearned <- cc1718full %>%
    mutate(topflag  = ifelse(TopCode==493013 & UnitsEarned <= UnitsAttempted| TopCode == 499900 & UnitsEarned <= UnitsAttempted, 1, 0))%>% 
  group_by(inter_segment_key, topflag) %>% summarise(sum(UnitsEarned)) %>% mutate(topunits = topflag * `sum(UnitsEarned)`) %>% group_by(inter_segment_key) %>% summarise(sum(topunits))

summary(topearned)



range(topearned$`sum(topunits)`, na.rm = T)

#merge topearned


```

```{r}
#transfer grades

ccgpa <- cc1718full %>% 
   #mutate(`UnitsEarned*` = ifelse(UnitsEarned < 88, UnitsEarned, 0)) %>%
  filter(UnitsEarned <= UnitsAttempted ) %>% 
  mutate(tflag  = ifelse(CreditFlag=="T" & UnitsAttempted > 0, 1, 0)) %>%
  group_by(inter_segment_key) %>% summarise(gpa = sum(gpaval*UnitsEarned)/sum(UnitsAttempted))

ccgpa_transferatt <- cc1718full %>% 
   #mutate(`UnitsEarned*` = ifelse(UnitsEarned < 88, UnitsEarned, 0)) %>%
  filter(UnitsEarned <= UnitsAttempted ) %>% 
  mutate(tflag  = ifelse(CreditFlag=="T" & UnitsAttempted > 0, 1, 0)) %>%
  filter(tflag==1) %>%
  group_by(inter_segment_key) %>% summarise(gpa = sum(gpaval*UnitsEarned)/sum(UnitsAttempted))

ccgpa <- cc1718full %>% 
  filter(CreditFlag == "T", UnitsEarned <= UnitsAttempted ) %>% 
  group_by(inter_segment_key) %>% summarise(gpa = sum(gpaval*UnitsEarned)/sum(UnitsAttempted))

summary(ccgpa)
#ccgpa <- courses1617 %>% group_by(derkey1) %>% summarise(mean(gpaval, na.rm=T))

#mean(ccgpa$`mean(gpaval, na.rm = T)`, na.rm=T)

#merge ccgpa & ccgpa_transferatt


```
```